Consumer Reviews and Product Discounts:\\ Evidence From Video Games

### 2020-08-09 Analysis/Code/Paper.Rmd
Added an option to create a hyperlink to the bibliography

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex

@@

```{r cache = F}
source(here("Analysis", "Code", "StructuralFunctions.R"))
load(here("Analysis", "Input", "info.Rda"))
load(here("Analysis", "Input", "panel.Rda"))
```

@@

```{r include = F,}
band <- 7

>>>>

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  latex_document:
    #keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true

@@

```{r cache = F}
knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")

source(here("Analysis", "Code", "StructuralFunctions.R"))
load(here("Analysis", "Input", "info.Rda"))
load(here("Analysis", "Input", "panel.Rda"))
```

@@

```{r include = F, cache=F}
band <- 7

### 2020-08-09 Analysis/Output/Paper.tex
Added an option to create a hyperlink to the bibliography

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
  pagebackref]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Dmitry Sorokin},
  colorlinks=true,
  linkcolor=mypink,
  filecolor=myblue,
  citecolor=mypink,
  urlcolor=mypink,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\renewcommand{\ttdefault}{cmr} % change the font of inline R results to normal
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        [Cited on page~#2.]%
    \else      [Cited on pages~#2.]%
    \fi}
\setlength{\parindent}{25pt}
\setlength{\parskip}{0pt}
\setlength{\skip\footins}{0.25cm} % margin before footnotes
\definecolor{myblue}{RGB}{31, 61, 122}
\definecolor{mypink}{RGB}{204, 0, 82}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]
\newcommand{\EE}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\PP}[1]{\mathbb{P}\left(#1\right)}
\newcommand{\CP}[2]{\mathbb{P}\left(#1 \,| \, #2 \right)}
\newcommand{\CE}[2]{\mathbb{E}\left[#1\,|\,#2 \right]}
\usepackage[bottom]{footmisc}
\usepackage[doublespacing]{setspace}
\usepackage[tableposition=top]{caption}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 08, 2020}

@@

 {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}

@@

\begin{table}[t]

\caption{\label{tab:transitionMatrix}Transition Probability And Count Matrices}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{ccccccccccccc}
\toprule
\multicolumn{6}{c}{Probabilities} & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Counts} \\
\cmidrule(l{3pt}r{3pt}){1-6} \cmidrule(l{3pt}r{3pt}){8-13}
Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos &   & Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos\\
\midrule
0 & 100 & 0 & 0 & 0 & 0 & Negative & 0 & 58 & 0 & 0 & 0 & 0\\
24 & 0 & 76 & 0 & 0 & 0 & Mixed & 60 & 0 & 189 & 0 & 0 & 0\\
0 & 43 & 0 & 25 & 33 & 0 & M. Positive & 0 & 245 & 0 & 141 & 188 & 0\\
0 & 0 & 40 & 0 & 60 & 0 & Positive & 0 & 2 & 207 & 0 & 310 & 0\\
0 & 0 & 84 & 0 & 0 & 16 & V. Positive & 0 & 0 & 220 & 0 & 0 & 43\\
0 & 0 & 0 & 0 & 100 & 0 & Ov. Positive & 0 & 0 & 0 & 0 & 25 & 0\\
\bottomrule
\end{tabular}}
\end{table}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}

@@

With the focus now on potential transitions, the crucial question is how
to define proximity to a transition. One approach would be to use the
raw review count, and to say that a game is close to upgrading its
review label when it needs five (ten, twenty \ldots) more positive
reviews to transition. However, given the heterogeneity in the
popularity of different games (see Figure \ref{sampleSizeHist}), five
extra reviews could be nothing for a very popular game, and hard to
acquire for a small game. For this reason I use a different approach,
that measures proximity by the expected number of days that a game has
to wait to accumulate the reviews necessary for a transition. In
particular, for every game-date pair I first measure how many positive
reviews that game needs at the moment to upgrade its review bin, and how
many negative reviews that game needs to degrade its review bin. In the
next step, for each game I calculate the average speed of review
arrivals, by simply dividing the number of positive (negative) reviews
as of the last day in the sample by the age of the game on that day.
Knowing the speed of positive and negative review arrivals, and the
number of reviews necessary for a transition, I then define the
proximity to a positive (negative) transition to be the expected number
of days needed for the game to accumulate the necessary number of
positive (negative) reviews, assuming that it does not receive any
negative (positive) reviews during that time.

@@

\hypertarget{nlls-estimator-of-beta}{%
\subsection{\texorpdfstring{NLLS estimator of
\(\beta\)}{NLLS estimator of \textbackslash beta}}\label{nlls-estimator-of-beta}}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[12pt,pagebackref]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdfauthor={Dmitry Sorokin},
            colorlinks=true,
            linkcolor=mypink,
            filecolor=myblue,
            citecolor=mypink,
            urlcolor=mypink,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\renewcommand{\ttdefault}{cmr} % change the font of inline R results to normal
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        [Cited on page~#2.]%
    \else      [Cited on pages~#2.]%
    \fi}
\setlength{\parindent}{25pt}
\setlength{\parskip}{0pt}
\setlength{\skip\footins}{0.25cm} % margin before footnotes
\definecolor{myblue}{RGB}{31, 61, 122}
\definecolor{mypink}{RGB}{204, 0, 82}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]
\newcommand{\EE}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\PP}[1]{\mathbb{P}\left(#1\right)}
\newcommand{\CP}[2]{\mathbb{P}\left(#1 \,| \, #2 \right)}
\newcommand{\CE}[2]{\mathbb{E}\left[#1\,|\,#2 \right]}
\usepackage[bottom]{footmisc}
\usepackage[doublespacing]{setspace}
\usepackage[tableposition=top]{caption}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 09, 2020}

@@

 {\centering \includegraphics[width=0.75\linewidth,]{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/steamStore}

@@

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/example-game-1}

@@

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}

@@

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}

@@

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}

@@

\begin{table}

\caption{\label{tab:transitionMatrix}Transition Probability And Count Matrices}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccccccccccccc}
\toprule
\multicolumn{6}{c}{Probabilities} & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Counts} \\
\cmidrule(l{3pt}r{3pt}){1-6} \cmidrule(l{3pt}r{3pt}){8-13}
Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos &   & Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos\\
\midrule
0 & 100 & 0 & 0 & 0 & 0 & Negative & 0 & 58 & 0 & 0 & 0 & 0\\
24 & 0 & 76 & 0 & 0 & 0 & Mixed & 60 & 0 & 189 & 0 & 0 & 0\\
0 & 43 & 0 & 25 & 33 & 0 & M. Positive & 0 & 245 & 0 & 141 & 188 & 0\\
0 & 0 & 40 & 0 & 60 & 0 & Positive & 0 & 2 & 207 & 0 & 310 & 0\\
0 & 0 & 84 & 0 & 0 & 16 & V. Positive & 0 & 0 & 220 & 0 & 0 & 43\\
0 & 0 & 0 & 0 & 100 & 0 & Ov. Positive & 0 & 0 & 0 & 0 & 25 & 0\\
\bottomrule
\end{tabular}}
\end{table}

@@

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}

@@

With the focus now on potential transitions, the crucial question is how
to define proximity to a transition. One approach would be to use the
raw review count, and to say that a game is close to upgrading its
review label when it needs five (ten, twenty \ldots{}) more positive
reviews to transition. However, given the heterogeneity in the
popularity of different games (see Figure \ref{sampleSizeHist}), five
extra reviews could be nothing for a very popular game, and hard to
acquire for a small game. For this reason I use a different approach,
that measures proximity by the expected number of days that a game has
to wait to accumulate the reviews necessary for a transition. In
particular, for every game-date pair I first measure how many positive
reviews that game needs at the moment to upgrade its review bin, and how
many negative reviews that game needs to degrade its review bin. In the
next step, for each game I calculate the average speed of review
arrivals, by simply dividing the number of positive (negative) reviews
as of the last day in the sample by the age of the game on that day.
Knowing the speed of positive and negative review arrivals, and the
number of reviews necessary for a transition, I then define the
proximity to a positive (negative) transition to be the expected number
of days needed for the game to accumulate the necessary number of
positive (negative) reviews, assuming that it does not receive any
negative (positive) reviews during that time.

@@

\hypertarget{nlls-estimator-of-beta}{%
\subsection{\texorpdfstring{NLLS estimator of
\(\beta\)}{NLLS estimator of \textbackslash{}beta}}\label{nlls-estimator-of-beta}}
